Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-11-01 manuscript.tex
20161101

\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. To overcome the limited input of the dynamic model, a new scalable dimensionless transform and strictly bounded terms are designed to guarantee the existence of the ratio between limited input and command signal. The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain, and the stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation to guarantee that the asymptotically stability of the deployment dynamics. The numerical simulations are reported to verify the effectiveness of the proposed control laws.
\end{abstract}
\begin{keyword}
Tethered satellite;  Sliding mode control;  Input limitation; Adaptive control
\end{keyword}
\end{frontmatter}
\section{Introduction}
The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique supports various applications for space exploration and scientific research, such as space debris removal, space elevator, satellite de-orbit and the tethered space robot~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}. Many international space research institutes have launched some orbital, suborbital and ground experiments in an effort, such as TSS-1R, SEDS, MAST and YES2, to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results make researchers proceed to advance mechanics, kinetic and control studies intensively, to tackle the challenges of requirements from space missions in the future~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.\par

Recent scientific researches on deployment of the tethered satellite focus on the stabilization of the dynamics, and have varying merit and outcomes, providing different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approach~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}. Among the deployment stabilization strategies, the hybrid tension and thruster control boosts to the new developments. Iki et al. implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and the thruster was used to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}. \textcolor{red}{Aslanov et al. presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system is excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al. investigated the attitude and deploying dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. Liu et al. equipped the thruster system, which consisted of four pairs of thrusters, in the subsatellite dedicating for regulation of the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages, the first stage of which ejected the tether with thruster to position the tether at desired beginning point of the second stage, and the second stage continued to adjust the tether to the stable vertical configuration by using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thrust-aided librating deployment of tape tethers, and the force acting on the tape tether included the tension and thruster force~\cite{mantellato2015thrust}. This hybrid strategy has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, thus is broadly utilized in reality compared with other control strategies.\par

There also exist some obstacles in the design of the hybrid control. Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical condition, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether. Also, the thruster can not provide infinite force~\cite{martinez1998spacecraft}. Hence the tension and thruster force for the deployment/retrevial are both limited, and in the view of control theory, the phenomena usually causes the input limitation of a dynamic system. Substituting limited inputs into unmodified conventional control scheme designed for unlimited input system results in lost of control or poor performance, and theoretically, such kind of implement is unreasonable. Hence to cope with input limitation in the tethered satellite system (TSS), some scientific researchers spent much effort on restricting input, providing many solutions on satellite arrangements and deployments. Huang et al. addressed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect of constrained input by using specific auxiliary design systems~\cite{huang2015adaptive}. Wen et al. took into account the positive bounded tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}. Liu et al. reported the variable structure scheme for the deployment with thruster control, where the thruster is used to guarantee the positive tension during the mission~\cite{yingying2012variable}. In summary, existed studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input. In aspect of designing elaborate limited inputs, as Wen et al. explained, the limited terms, including the tension and the state of the deployment, can be viewed as the solution of a nonlinear optimal control \cite{wen2015tension}. Hu reported an adaptive sliding mode control with saturated input by using reduced sliding dynamic design approach \cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits. In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the tethered satellite system is studied. For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function. Based on the feature of the saturated command, an adaptive rate is introduced into the controller design to remove the effect of the input limitation theoretically. In order to improve the performance of the sliding phase, the terminal attractor is incorporated into the design of the ideal sliding surface. Numerical simulations are performed to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par
The paper is organized as follows: Section \ref{sec:2} introduces the standard mathematical model of the deployment of the TSS. Section \ref{sec:3} designs the adaptive saturated sliding mode control laws with input limitation for the dynamics, and these simulations are exhibited in Section \ref{sec:4} to reveal the effectiveness and efficiency. The conclusion is given in Section \ref{sec:5}.

@@

In the analysis of the deployment of the TSS, there is a primary assumption that the movement of entire system is approximating to a ``rolling ball'' behavior with three DOFs modelled, and reasonably one can invoke the spherical coordinates to describe the behavior. During space mission, the mass of the tether is much smaller than that of the mother satellite, and hence it is always ignored sufficiently. Some other assumptions are obvious throughout the analysis, and listed in the following. A satellite is able to be regard as a particle under the condition that the length of the tether is large enough, and due to the tiny ratio of the mass between the satellites, the deployment of the subsatellite will not effect the motion of the mother satellite and keep the nominal orbit during the whole mission. The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
Before giving out the model, some preliminary symbols are exhibited. $R_0$ is a positive scaler meaning the radius of orbit without disturbance, and $\Omega = \sqrt{\mu_e/R_0^3}$ is the orbital angular velocity where $\mu_e$ is the coefficient of the Earth gravity field.\par

@@

\textcolor{red}{where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively. $(\cdot)'$ represents the differentiation with respective to time, and $l$ means the tether length connecting the satellites. $\theta$ and $\phi$ depict the rolling and pitching dynamics of the TSS. For clarity, $m_1m_2/m$ is rewritten as $\bar m$. $\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_\theta d$ and $\tau_\phi d$ stand for the bounded external disturbances. Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:

@@

In reality, once $\lambda = 0$ establishes, the mother satellite and subsatellite collide with each other. Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the satellites in reasonably safe formation, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:varcon}) theoretically. $\lambda_{max}$ stands for the maximum tether length ratio.\par
Tension in a tether is a positive scalar quantity during the deployment, since zero tension is slack, which is inconsistent with the fundamental assumption that the tether is stiff in the ``rolling ball'' model. $\tau_{tmax}$ denotes the maximum tensile tolerance of the tether, and $\tau_t>\tau_{tmax}$ may leads to the break of tether. Hence, $\tau_{tmin}$ can be a small value to guarantee the stiff tether, and reasonable $\tau_{tmax}$\ prevents fracture of tether.

@@

At this point the deployment dynamics with input limitation has been established, and an adaptive saturated sliding mode  control will be presented in the subsequent section.

@@

Before declaring the controller design, some basic precondition is prepared for proceeding derivation.  The left side of Eq.~(\ref{eq:dynamic model}) is able to be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(\bm q,\dot {\bm q},\ddot {\bm q})$ consists of known nonlinear functions. $\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form. Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot{\bm q}_r$~\cite{parra2003dynamic}:

@@

where $Y_r = Y_r(\bm q,\dot{\bm q},\dot{\bm q}_r,\ddot{\bm q}_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $\bm S_r$ is able to be obtained, as follows:

@@

The process above can frame a conventional dynamic sliding PID control scheme, which can regulate the dynamics of n-link robotic manipulator if extending the dimension in the derivation above \cite{parra2003dynamic}. However, it is not able to regulate the dynamics of the deployment as desired theoretically, because the input $\tau$ in the PID controller is not confined to the characteristics of the tension. For coping with the issue about the bounded input, we develop the dynamic sliding mode control with the experience of saturated manifold, which is also a popular technique in the control of Lagrangian system.\par

@@

\bm\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1})),\label{eq:slider control}

@@

where $K_1\in R^{3\times 3}$ is a positive define diagonal matrix, which will be given out later, and if $K\in R^{3\times 3}$, define

@@

\textcolor{red}{$\varphi$ is the boundedness of the lumped uncertainty. $\gamma$ is designed as a time-varying positive scalar, $\varphi>1$ is the designer parameter, such that the deployment dynamics can be regulated as desired.}

@@

    where $\gamma_0$ can be selected as $\gamma_0=0.1$, such that $\gamma\int_{t_0}^t\bm S_{q1}d\varsigma$ is guaranteed to satisfy $\gamma\int_{t_0}^t\bm S_{q1}d\varsigma\in[-1,1]$.}\par

@@

Since the command $ -\delta\varphi F(t) \bm S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ such that $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:

@@

$v\dot v$ is able to be derived as follows:

@@

utilizing $\bm{sign}(\bm S_{r1})=\bm{sign}(\bm S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:

@@

@@

where a large enough $\delta>1$ can be selected such that $\dot V \le 0$. According to the description of Barbalat¡¯s lemmas, it implies that $\bm S_{r2}$ asymptotically converges to origin. Also, the finite convergent time of desired sliding surface can be calculated by referring to~\cite{Ma201667}.}\par

@@

and for employing Lyapunov second method to analyse the stabilities of $\bm S_{q2}$ and $\Delta\bm q$, we firstly select a Lyapunov function candidate

@@

where $0<p/q<1$ and $p$ and $q$ are both positive odd, and a shrewd formula

@@

where $0<\hat \alpha<1$, performs the same behavior. Inducting the terminal attractor into the saturated sliding mode control yields a saturated slider-like scheme, and for adopting to the system subject to input limitation, an assumption is given firstly.

@@

If the designer parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control degenerates into the quasi-saturated sliding mode control. Compared with the saturated sliding mode control, $\bm S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method. This is because the establishment of the equation $\dot {\bm S}_{q3} = \gamma\vert \bm S_{q3}\vert^{\hat\alpha} \bm{ sign}(\bm S_{q3})$.

@@

Assumption~\ref{as:1} guarantees that the input $\tau$ is bounded in Theorem~\ref{thm:2}, accordingly, a tiny positive scalar $c$ is able to be found such that $0<c\le R(\hat\tau_t)<1$ always exists. Admittedly, such kind of assumption is ''skillful'', but meaningful to arbitrary controllable dynamics in reality. It is reasonable to propose the terminal sliding mode control for the dynamics as follows:

@@

such that the finite convergence of the system~(\ref{eq:Sr4}) can be ensured by using terminal sliding mode theory. $\varphi$ is the boundedness of the lumped uncertainty, and can be obtained by referring to Theorem~\ref{thm:1}.

@@

In this section, the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively. The parameters of these controllers can selected as follows: $\delta=1.1$, $\varphi= 1\times 10^{-3}$, $\alpha = 0.8$, $\gamma = 0.1$ and $\hat\alpha=0.6$.\par
Besides the designer parameter determined, the simulation initial and desired condition can be described as follows. The circular orbital altitude is selected around 260 $km$ approximately, and the orbital angular velocity is about $1.17\times 10^{-3}$ $rad/s$. At the initial ejection of the subsatellite, the true anomaly is assumed 0 $rad$. Meanwhile, the initial deployment velocity is about 3 $m/s$, and the subsatellite is going to be deployed at 3.5 $km$ vertically. The pitching and rolling dynamics is varying in a small range, and hence, without loss of generality, the numerical initial condition gives rise to: $\theta_0 = 0.1$, $\phi_0 = 0.1$, $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$. Hence the dimensionless tether length is varying in $[0.02,1]$.\par

@@

Based on the expression above, one can obtain $\bar{m}\Omega^2L\approx 4.79\times 10^{-3}$, and suitable bounded values $\hat\tau_{tmin}$ and $\hat\tau_{tmax}$ can be chosen to make the dimensionless tension $\hat\tau_t$ fall in the region $[-3,0.01]$.\par
At this point, the simulations of the deployment dynamics of the TSS are able to be carried on. \textcolor{red}{We firstly conduct the simulation about the pure deployment dynamics without any uncertainties to verify the effectiveness of the proposed control laws, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}.} Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that the all the methods finish the deployment in aspect of the tether length. ST-SMC and QST-SMC complete the deployment at about 4 $rad$, and from Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, and hence the curves of the tether length climb more rapidly at the beginning. In contrary, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$. This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to origin more early than S-SMC and QST-SMC.\par
The in-plane and out-of-plane angles reflect the swinging dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}. For ST-SMC, the in-plane dynamics is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time, and hence the coalition of the length and the swinging dynamics implies that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC. S-SMC makes the tether swing to desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) is exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently. Thanks to the scalable dimensionless transform determined conservatively, the tension exerted on the tether falls in the reasonable region.\par

>>>>

\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. \textcolor{red}{To overcome the limited inputs of the dynamic model, a new scalable dimensionless transformation and strictly bounded terms are designed, which guarantee the existence of the ratio between limited inputs and command signals.} The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain. The stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation and guarantee the asymptotically stability of the deployment dynamics. \textcolor{red}{Finally, numerical simulations are presented to verify the effectiveness of the proposed control laws.}
\end{abstract}
\begin{keyword}
Tethered satellite;  Sliding mode control;  Input limitation; Adaptive control
\end{keyword}
\end{frontmatter}
\section{Introduction}
The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space exploration and scientific research, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}. \textcolor{red}{Many international space research institutes have launched some orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.}\par

\textcolor{red}{Recent scientific researches about deployment of the tethered satellite system focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.} Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the tethered satellite system. Iki et al. implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and utilized the thruster to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}. \textcolor{red}{Aslanov et al. presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al. investigated the attitude and deployment dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. \textcolor{red}{Liu et al. equipped the subsatellite with the thruster system, consisting of four pairs of thrusters, in order to regulate the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages: in the first stage, the thruster was used to eject to the desired starting point of the next stage, and in the second stage, the tether was adjusted to the stable vertical configuration using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thrust-aided deployment of tape tethers driven by both the tension and thruster force~\cite{mantellato2015thrust}. These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.}\par

There also exist some obstacles in the hybrid control design. Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical conditions, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether. Also, the thruster can not provide infinite force~\cite{martinez1998spacecraft}. Hence the tension and thruster force for the deployment/retrievial are both limited, and in the view of control theory, the phenomena usually causes the input limitation of a dynamic system. Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable. Hence to cope with input limitation in the tethered satellite system (TSS), many scientific researchers spent much effort on restricting input, providing many solutions on satellite arrangements and deployments. Huang et al. proposed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect of constrained input by using specific auxiliary design systems~\cite{huang2015adaptive}. Wen et al. took into account the positive bounded tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}. Liu et al. reported the variable structure scheme for the deployment with thruster control, where the thruster is used to guarantee the positive tension during the mission~\cite{yingying2012variable}. In summary, existing studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input. In aspect of designing elaborate limited inputs, as Wen et al. explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as the solution of a nonlinear optimal control issue~\cite{wen2015tension}. \textcolor{red}{Hu reported an adaptive sliding mode control law with saturated input by using reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the tethered satellite system is studied. For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function. Based on the feature of the saturated command, an adaptive rate is introduced into the controller design to remove the effect of the input limitation theoretically. In order to improve the performance of the sliding phase, the terminal attractor is incorporated into the design of the ideal sliding surface. We perform numerical simulations to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par
The paper is organized as follows: Section~\ref{sec:2} introduces the standard mathematical model of the deployment of the TSS. Section~\ref{sec:3} designs the adaptive saturated sliding mode control laws with input limitation for the dynamics, and these simulations are exhibited in Section~\ref{sec:4} to reveal the effectiveness and efficiency. The conclusion is given in Section~\ref{sec:5}.

@@

\textcolor{red}{In the analysis of the deployment of the TSS, there is a primary assumption that the movement of entire system is similar to a ``rolling ball'' behavior with three DOFs modelled, and it is reasonable to invoke the spherical coordinates to describe the behavior.} During space mission, the mass of the tether is much smaller than that of the mother satellite, and hence it is always ignored sufficiently. Some other assumptions are obvious and as follows. \textcolor{red}{The sizes of satellites are small compared with the length of the tether, and hence a satellite can be regard as a particle if the tether is long enough. Typically, the mass ration between mother satellite and subsatellite, i.e., in YES2, the mother satellite mass is 6530~$kg$, and the subsatellite mass is 12~$kg$~\cite{Williams2008}. Due to the tiny mass ratio between the satellites, the deployment of the subsatellite will not affect the motion of the mother satellite and keep the nominal orbit during the whole mission.} The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
Symbols used in the model are defined as follows. $R_0$ is a positive scaler meaning the radius of orbit without disturbance, and $\Omega = \sqrt{\mu_e/R_0^3}$ is the orbital angular velocity where $\mu_e$ is the coefficient of the Earth gravity field.\par

@@

\textcolor{red}{where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively. \textcolor{red}{$(\cdot)'$ represents a first derivative with respect to time, and $l$ means the tether length connecting the satellites. $\theta$ and $\phi$ depict the roll and pitch dynamics of the TSS. For clarity, $m_1m_2/m$ is rewritten as $\bar m$. $\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:

@@

\textcolor{red}{In reality, once $\lambda = 0$ is satisfied, the mother satellite and subsatellite will collide with each other. Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the reasonably safe formation of the satellites, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:varcon}) theoretically.} $\lambda_{max}$ stands for the maximum tether length ratio.\par
Tension in a tether is a positive scalar quantity during the deployment, since zero tension means slack, which is inconsistent with the fundamental assumption that the tether is stiff in the ``rolling ball'' model. $\tau_{tmax}$ denotes the maximum tensile tolerance of the tether, and $\tau_t>\tau_{tmax}$ may leads to the break of tether. Hence, $\tau_{tmin}$ can be a small value to guarantee the stiff tether, and reasonable $\tau_{tmax}$\ prevents fracture of tether.

@@

This section have established the deployment dynamics with input limitation and an adaptive saturated sliding mode  control will be presented in the subsequent section.

@@

Before declaring the controller design, some basic precondition is prepared for proceeding derivation.  The left side of Eq.~(\ref{eq:dynamic model}) can be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(\bm q,\dot {\bm q},\ddot {\bm q})$ consists of known nonlinear functions. $\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form. Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot{\bm q}_r$~\cite{parra2003dynamic}:

@@

where $Y_r = Y_r(\bm q,\dot{\bm q},\dot{\bm q}_r,\ddot{\bm q}_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $\bm S_r$ can be obtained, as follows:

@@

The process above can frame a conventional dynamic sliding PID control scheme, which can regulate the dynamics of n-link robotic manipulator if the dimension in the derivation above is extended~\cite{parra2003dynamic}. However, it is not possible to regulate the dynamics of the deployment as desired theoretically, because the input $\tau$ in the PID controller is not confined to the characteristics of the tension. To cope with the issue about the bounded input, we develop the dynamic sliding mode control with the experience of saturated manifold, which is also a popular technique in the control of Lagrangian system.\par

@@

\bm\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1})),\label{eq:slider control}

@@

\textcolor{red}{where $K_1\in R^{3\times 3}$ is a positive definite diagonal matrix, which will be given out later, and if $K\in R^{3\times 3}$, define}

@@

\textcolor{red}{$\varphi$ is the boundedness of the lumped uncertainty. $\gamma$ is designed as a time-varying positive scalar and $\varphi>1$ is the design parameter, so that the deployment dynamics can be regulated as desired.}

@@

    where $\gamma_0$ can be selected as $\gamma_0=0.1$.}\par

@@

\textcolor{red}{Since the command $ -\delta\varphi F(t) \bm S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ which satisfy $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:}

@@

\textcolor{red}{$v\dot v$ can be derived as follows:

@@

considering $\bm{sign}(\bm S_{r1})=\bm{sign}(\bm S_{r2})$ and $K_1$, we can proceed to rewrite Eq.~(\ref{eq:V1_1}) as:

@@

\end{align}}

@@

where a large enough $\delta>1$ can be selected to satisfy $\dot V \le 0$. According to the description of Barbalat¡¯s lemmas, we can conclude  that $\bm S_{r2}$ asymptotically converges to origin. Also, the finite convergent time of desired sliding surface can be calculated by referring to~\cite{Ma201667}.}\par

@@

and for employing Lyapunov second method to analyse the stabilities of $\bm S_{q2}$ and $\Delta\bm q$, we firstly select a Lyapunov candidate function

@@

\textcolor{red}{where $0<p/q<1$ while $p$ and $q$ are both positive odd, and a equivalent formula}

@@

\textcolor{red}{where $0<\hat \alpha<1$, performs the same behavior. Putting the terminal attractor into the saturated sliding mode control yields a saturated slider-like scheme, and before introducing the input limitation into the system, an assumption is given firstly.}

@@

If the design parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control degenerates into the quasi-saturated sliding mode control. Compared with the saturated sliding mode control, $\bm S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method. This is because the establishment of the equation $\dot {\bm S}_{q3} = \gamma\vert \bm S_{q3}\vert^{\hat\alpha} \bm{ sign}(\bm S_{q3})$.

@@

\textcolor{red}{Assumption~\ref{as:1} guarantees that the input $\tau$ is bounded in Theorem~\ref{thm:2}, accordingly, a tiny positive scalar $c$ can be found to ensure that $0<c\le R(\hat\tau_t)<1$ always exists.} Admittedly, such kind of assumption is ''skillful'', but meaningful to arbitrary controllable dynamics in reality. It is reasonable to propose the terminal sliding mode control for the dynamics as follows:

@@

so that the finite convergence of the system~(\ref{eq:Sr4}) can be ensured by using terminal sliding mode theory. $\varphi$ is the boundedness of the lumped uncertainty, and can be obtained by referring to Theorem~\ref{thm:1}.

@@

This section presents the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively. The parameters of these controllers can be selected as follows: $\delta=1.1$, $\varphi= 1\times 10^{-3}$, $\alpha = 0.8$, $\gamma = 0.1$ and $\hat\alpha=0.6$.\par
Besides the design parameter determined, the simulation initial and desired condition can be described as follows. The circular orbital altitude is selected around 260 $km$ approximately, and the orbital angular velocity is about $1.17\times 10^{-3}$ $rad/s$. At the initial ejection of the subsatellite, the true anomaly is assumed to be 0 $rad$. Meanwhile, the initial deployment velocity is about 3 $m/s$, and the subsatellite is going to be deployed at 3.5 $km$ vertically. \textcolor{red}{The pitch and roll dynamics is varying in a small range, and hence, without loss of generality, the numerical initial condition gives rise to: $\theta_0 = 0.1$, $\phi_0 = 0.1$, $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$. Hence the dimensionless tether length is in the range of $[0.02,1]$.}\par

@@

Based on the expression above, one can obtain $\bar{m}\Omega^2L\approx 4.79\times 10^{-3}$, and suitable boundary values $\hat\tau_{tmin}$ and $\hat\tau_{tmax}$ can be chosen to make the dimensionless tension $\hat\tau_t$ fall in the region $[-3,0.01]$.\par
At this point, the simulations of the deployment dynamics of the TSS can be carried on. \textcolor{red}{We firstly conduct the simulation about the pure deployment dynamics without any uncertainties to verify the effectiveness of the proposed control laws, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}. Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that all the methods can realize the deployment in aspect of the tether length.} ST-SMC and QST-SMC complete the deployment at about 4 $rad$. \textcolor{red}{As shown in Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, indicating the curves of the tether length climb more rapidly at the beginning.} However, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$. This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to origin earlier than S-SMC and QST-SMC.\par
\textcolor{red}{The in-plane and out-of-plane angles reflect the swing dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.} For ST-SMC, the in-plane dynamics is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time. \textcolor{red}{Hence the coalition of the length and the swing dynamics implies that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC.} S-SMC makes the tether swing to desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) is exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently. Thanks to the scalable dimensionless transformation determined conservatively, the tension exerted on the tether falls in the reasonable region.\par
